Title

### 2014-11-14 manuscript.tex
Added some figures to the text

\citet{Grombein2013} provides Cartesian kernels for the tesseroid volume
internals that define the gravitational potential, gravitational attraction,
and Marussi tensor (EQUATIONS).
\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell} \kappa  dr' d\phi' d\lambda',
    \label{eq:tesspot}
\end{equation}
\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta\alpha}{\ell^3} \kappa dr' d\phi' d\lambda',
    \label{eq:tessgrav}
\end{equation}
\noindent
and
\begin{equation}
    g_{\alpha\beta}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        I_{\alpha\beta}
        dr' d\phi' d\lambda',
    \label{eq:tesstensor}
\end{equation}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature
        (i.e., the GLQ order).
        Black circles represent the horizontal location of the GLQ nodes
        (not shown for GLQ order 30).
        a) Field calculated at $400\ km$ height using GLQ order 2.
        The effect is similar to that presented by \citet{Asgharzadeh2007}.
        b) At $150\ km$ height and order 2,
        the field resembles that of
        four point sources located at the GLQ nodes.
        This effect was shown by \citet{Ku1977}
        for the case of the $g_z$ component of a right rectangular prism.
        c) At $150\ km$ but with a higher GLQ order of 30,
        the field is similar to that expected for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical evaluation of the accuracy}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

>>>>

A tesseroid is a spherical mass element defined in geocentric coordinates
(Figure~\ref{fig:tesseroid}).
It is bounded by two meridians, two parallels, and two concentric circles.
The gravitational fields of a tesseroid at a point $P = (r,\phi,\lambda)$
are determined with respect to the local North-oriented coordinate system at
P (x, y, z in Figure~\ref{fig:tesseroid}).
Notice that this is a left-handed coordinate system.

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

\citet{Grombein2013} provides Cartesian kernels for the tesseroid volume
internals that define the gravitational potential, gravitational attraction,
and Marussi tensor, respectively,

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell} \kappa  dr' d\phi' d\lambda',
    \label{eq:tesspot}
\end{equation}
\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta\alpha}{\ell^3} \kappa dr' d\phi' d\lambda',
    \label{eq:tessgrav}
\end{equation}
\noindent
and
\begin{equation}
    g_{\alpha\beta}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        I_{\alpha\beta}
        dr' d\phi' d\lambda'.
    \label{eq:tesstensor}
\end{equation}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature
        (i.e., the GLQ order).
        Black circles represent the horizontal location of the GLQ nodes
        (not shown for GLQ order 30).
        a) Field calculated at $400\ km$ height using GLQ order 2.
        The effect is similar to that presented by \citet{Asgharzadeh2007}.
        b) At $150\ km$ height and order 2,
        the field resembles that of
        four point sources located at the GLQ nodes.
        This effect was shown by \citet{Ku1977}
        for the case of the $g_z$ component of a right rectangular prism.
        c) At $150\ km$ but with a higher GLQ order of 30,
        the field is similar to that expected for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figs/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $d$ is the Cartesian distance between
        the center of the top face of the tesseroid
        and $P$.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:ratio}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation of the accuracy}

@@
